---
title: "HW7"
format: pdf
editor: visual
---

Homework7

## 

1.How can you check for missing values (NA) in the **`fert_cons_data`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** dataset? Please provide the R code and give a brief explanation of what is happening in the code.

```{r missing, warning=FALSE}
library(WDI)
library(tidyr)
library(dplyr)
# Gather fertilizer consumption data from WDI
fert_cons_data <- WDI(indicator = "AG.CON.FERT.ZS")
missing_values <- is.na(fert_cons_data)
missing_count <- colSums(missing_values)
print(missing_count)
# This function returns a logical matrix with the same dimensions as fert_cons_data, where each element is TRUE if the corresponding element in fert_cons_data is NA, and FALSE otherwise.
```

2.  What is the purpose of reshaping the **`fert_cons_data`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** dataset into a wide format?

    The purposes of reshaping may include simplify visualization, summary statistics, comparative analysis, modeling, and data export, but the decision to reshape format should be based on the specific analytical needs.

    ```{r reshaping}
    # Reshape fert_cons_data to year wide-format
    fert_wide <- tidyr::pivot_wider(fert_cons_data,
    names_from = year,values_from = AG.CON.FERT.ZS)
    ```

3.  How can you rename the columns **`Year`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** and **`Fert`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** in the **`fert_long`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** dataset? Please provide the R code and give a brief explanation of what is happening in the code.

    ```{r}
    # gather a fert_long dataset
    fert_long <- tidyr::pivot_longer(fert_wide, cols = `2016`:`2010`, names_to = "Year", values_to = "Fert")
    # to rename year and fert_cons columns 
    fert_long <- dplyr::rename(fert_long, 
                              year = Year, 
                              fert_cons = Fert)
    head(fert_long)
    # have the fert_long_sub dataset by drop outliers
    fert_long_sub <- subset(x = fert_long, fert_cons <= 1000)
    ```

4.  What function is used to create a density plot of the **`fert_cons`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** variable in the **`fert_long`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** dataset? Please provide the R code and give a brief explanation of what is happening in the code.

    ```{r plot}
    library(ggplot2)
    # Create density plot
    ggplot(data = fert_long_sub, aes(fert_cons)) +
      geom_density() + 
      xlab("Fertilizer Consumption") + 
      ylab("Density") +
      theme_bw()
    ```

5.  How can you recode the country name "Korea, Rep." to "South Korea" in the **`fert_long_sub`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** dataset? Please provide the R code and give a brief explanation of what is happening in the code.

    ```{r}
    # Recode country == "Korea, Rep." to "South Korea"
    fert_long_sub$country[fert_long_sub$country ==
    "Korea, Rep."] <- "South Korea" 
    head(fert_long_sub)
    ```

6.  How is the **`fert_cons_log`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** variable created in the **`fert_long_sub`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** dataset? Please provide the R code and give a brief explanation of what is happening in the code.

    ```{r}
    #make a new variable based on the old variable 
    fert_long_sub$fert_cons_log <- log(fert_long_sub$fert_cons)
    summary(fert_long_sub$fert_cons_log)
    ```

7.  What is the purpose of creating the **`fert_cons_group`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** variable in the **`fert_long_sub`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** dataset?

    ```{r}
    # The purpose is to create numeric factor levels variable
    # Attach fert_long_sub data frame
    attach(fert_long_sub)
    # Created new fert_cons_group variable based on # fert_cons
    fert_long_sub$fert_cons_group[fert_cons < 18] <- 1
    fert_long_sub$fert_cons_group[fert_cons >= 18 & fert_cons < 81] <- 2
    fert_long_sub$fert_cons_group[fert_cons >= 81 & fert_cons < 158] <- 3
    fert_long_sub$fert_cons_group[fert_cons >= 158] <- 4
    fert_long_sub$fert_cons_group[is.na(fert_cons)] <- NA
    # Detach data frame
    detach(fert_long_sub)
    summary(fert_long_sub$fert_cons_group)
    ```

8.  How can you convert the **`fert_cons_group`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** variable into a factor variable with labels "low", "medium low", "medium high", and "high"? Please provide the R code and give a brief explanation of what is happening in the code.

    ```{r}
    # Create vector of factor level labels
    fc_labels <- c("low", "medium low", "medium high", "high")
    # Convert fert_cons_group to a factor
    fert_long_sub$fert_cons_group <- factor(fert_long_sub$fert_cons_group, labels = fc_labels)
    ```

9.  What is the purpose of using the **`countrycode`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** package in the **`iso2c`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** variable creation?\
    The **`countrycode`** package in R is used to convert country names or codes into ISO 3166-1 alpha-2 country codes, providing consistency and compatibility for data analysis across different datasets or systems.

10. How can you merge the **`fin_regulator`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}**, **`disprop_data`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}**, and **`fert_long_sub`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** datasets based on the **`iso2c`{style="font-family: arial, helvetica, sans-serif; text-shadow: none !important; letter-spacing: normal !important; margin: 0px; padding: 0px; border: 0px; outline: 0px; font-weight: inherit; font-style: inherit; font-size: 13.3333px;"}** variable? Please provide the R code and give a brief explanation of what is happening in the code.

    ```{r}
    library(rio)
    # Place the URL into the object fin_url
    fin_url <- "https://bit.ly/2xlQ2j5"
    # Download data
    fin_regulator <- import(fin_url, format = "csv")
    # load countrycode 
    library(countrycode)
    fin_regulator$iso2c <- countrycode(fin_regulator$country,
    origin = "country.name", destination = "iso2c")
    head(fin_regulator)

    # Place shortened URLinto url object
    url <- "http://bit.ly/14aSjxB"
    # Download data
    disprop_data <- rio::import(url, format = "csv")
    # Show variable names
    names(disprop_data)

    # Merge fin_regulator and disprop_data
    merged_data_2 <- merge(fin_regulator, disprop_data, union("iso2c", "year"), all = TRUE)
    # Merge combined data frame with fert_long_sub
    merged_data_2 <- merge(merged_data_2, fert_long_sub, union("iso2c", "year"), all = TRUE)
    names(merged_data_2)
    ```

The link to Github repository: https://github.com/weiziwu/Week_7_HW.git
